Distributed Behavior in a Fluid Analogy Architecture

### 2017-12-10 papers/draft.tex
Fixes sources + adds makefile

This paper stems from Melanie Mitchell's (1993) and Douglas Hofstadter's \& FARG's (1995) work on the copycat program. 
This project focuses on effectively simulating intelligent processes through increasingly distributed decision-making.
In the process of evaluating the distributed nature of copycat, this paper also proposes a "Normal Science" framework. 
Copycat's behavior is based on the "Parallel Terraced Scan," a humanistic-inspired search algorithm.
The Parallel Terraced Scan is, roughly, a mix between a depth-first and breadth-first search.
To switch between modes of search, FARG models use the global variable \emph{temperature}.
\emph{Temperature} is ultimately a function of the workspace rule strength then the importance and happiness of each workspace structure.
Therefore, \emph{temperature} is a global metric, but is sometimes used to make local decisions.
Since copycat means to simulate intelligence in a distributed nature, it should make use of local metrics for local decisions.
This paper explores the extent to which copycat's behavior can be improved through distributing decision making.

@@

        [Summary of introduction, elaboration based on results]
        Let's cite! The Einstein's journal paper \cite{einstein} and the Dirac's
        book \cite{dirac} are physics related items.

>>>>

This paper stems from Melanie Mitchell's (1993) and Douglas Hofstadter's \& FARG's (1995) work on the copycat program. 
\cite{geb}
This project focuses on effectively simulating intelligent processes through increasingly distributed decision-making.
In the process of evaluating the distributed nature of copycat, this paper also proposes a "Normal Science" framework. 
Copycat's behavior is based on the "Parallel Terraced Scan," a humanistic-inspired search algorithm.
The Parallel Terraced Scan is, roughly, a mix between a depth-first and breadth-first search.
To switch between modes of search, FARG models use the global variable \emph{temperature}.
\emph{Temperature} is ultimately a function of the workspace rule strength then the importance and happiness of each workspace structure.
Therefore, \emph{temperature} is a global metric, but is sometimes used to make local decisions.
Since copycat means to simulate intelligence in a distributed nature, it should make use of local metrics for local decisions.
This paper explores the extent to which copycat's behavior can be improved through distributing decision making.

@@

        [Summary of introduction, elaboration based on results]
        %%Let's cite! The Einstein's journal paper \cite{einstein} and the Dirac's
        %%book \cite{dirac} are physics related items.
